The problem and promise of scale in multilayer animal social networks

### 2020-02-12 paper/manuscript.Rmd
hab sel start conclusion

>>>>

Multilayer networks can be combined to consider habitat selection, across scales

Animal social systems can be parsed by spatial contexts, defined by habitat types or connectivity, each represented in a layer within a multilayer framework
Seasonality of resources can be directly measured by investigating differences in habitat selection and sociality between seasonal layers

Taken together, these novel and explicit integrations of habitat selection and space use in multilayer netwokr
